\problem{}
Suppose $n$ contestants will participate in a set of contests $G$.  In each contest the contestants are split into two teams, possibly of different sizes, and such that each team contains at least one contestant.  We require that for any two contestants, there is some contest in $G$ in which these contestants are on different teams.  Design the contests in $G$ in order to minimize the total number of contests $|G|$.

\solution{}

Given each contestant a number $0,1,2,3,\cdots,n$. We can do binary decomposition to each number.
Suppose $n=2^k-1$, i.e. $k=\log_{2}{n-1}$. For the $i$-th contestant, the binary decomposition of $i$ is $b_{k-1}b_{k-2}\cdots b_0$.\\
We totally set $k$ contests.
For the $j$-th contest($j=0,1,\cdots,k-1$), if the $i$-th contestant has $b_j=0$, then we devide him into team $1$, otherwise team $2$.\\
So total $k=O(\log n)$ contests are hold, and each contestant must have at least one contest has different group with other contestants.\\

Proof:
\begin{itemize}
    \item correctness:\\
    $\forall x\neq y$, where $x$ and $y$ are the contestants' number. Then the binary decomposition of $x,y$ must have at least one digit difference.
    And according to the policy above, the two contestants must be in different teams at the contest that they has different digit.\\
    So all contestants must have at least one contest in different teams.
    \item minimize:\\
    Suppose that we totally has $t<k$ contests. Suppose the number of the contests are $0,1,\cdots, t-1$, then for each contest $i$, if the contestant $j$
    is in team $1$, then we mark $j$'s $i$-th digit to be $0$, otherwise, mark it to be $1$.\\
    So with this marking policy, since each contestants has at least one contest in different teams, so their marked sequence must be different. We can regard each 
    sequence as a binary number, so each contestant is given a unique number.\\
    But there are at most $2^t-1<2^k-1=n$ numbers, so it is impossible to has at least $t<k$ contests.\\
    So $k=\lceil\log n\rceil$ is the minimized number of contests.
\end{itemize}

So above all, the minimized total number of contests $|G|$ is $\lceil\log n\rceil$.\\

\newpage