\problem{}
A thief is planning to rob houses along a street. Each house has a certain amount of money stashed, and the thief can rob any set of houses, as long as he does not rob any adjacent houses.  Determine the maximum amount of money the thief can steal.
\solution{}

Suppose there are totally $n$ houses. Let $dp(i,0)$ be the maximum amount of money the thief can steal from the first $i$ houses without robbing the $i$-th house, and $dp(i,1)$ be the maximum amount of money the thief can steal from the first $i$ houses with robbing the $i$-th house.

For the initial condition, we have $dp(1,0)=0$ and $dp(1,1)=a_1$. As if the theif do not steal from the first house, he would get no money, and if he steals from the first house, he would get $a_1$ money.
And other states are set to be $0$. 

Then we have the following recursive formula:

If the theif does not steal from the $i$-th house, he can decide whether to steal from the $(i-1)$-th house or not. So he just need to make the optimal choice,
i.e. $dp(i,0)=\max\{dp(i-1,0),dp(i-1,1)\}$.

If the theif steals from the $i$-th house, he must not steal from the $(i-1)$-th house. i.e. $dp(i,1)=dp(i-1,0)+a_i$.

Finally, the maximum amount of money the thief can steal is $\max\{dp(n,0),dp(n,1)\}$.\\
As he can choose to steal from the $n$-th house or not. And the final decision is the maximum amount of money he can steal from the first $n$ houses.

The pseudo-code is shown in Algorithm \ref{alg:problem-3}. For loop in the pseudo-code in form `$\textbf{for } i \gets 1 \textbf{ to } n$' represents $i=1,2,\cdots,n$ sequentially.
\begin{algorithm}
    \caption{Maximum stolen money}
    \begin{algorithmic}[1]
    \State \textbf{Input:} Number of house $n$, each house's money number $a_1, a_2, \cdots, a_n$. 
    \State \textbf{Output:} The maximum number of money could steal $ans$.
    \State $dp(1,0) \gets 0, dp(1,1)\gets a_1$
    \For{$i \gets 2$ \textbf{to} $n$}
        \State $dp(i,0) \gets \max\{dp(i-1,0),dp(i-1,1)\}$
        \State $dp(i,0) \gets dp(i-1,0)+a_i$
    \EndFor
    \State $ans \gets \max\{dp(n,0),dp(n,1)\}$
    \State \textbf{return} $ans$
    \end{algorithmic}
    \label{alg:problem-3}
\end{algorithm}\\
The time complexity is $O(n)$.
The space complexity is $O(n)$.

\newpage