\problem{}

Given a set $C$, a collection of subsets of $C$ and an integer $k \geq 1$, the Set-Cover problem asks whether there are at most $k$ subsets from the collection which cover $C$, i.e. whose union includes all of $C$. Show that Set-Cover is NP-complete. Do not use a reduction from a problem which is very similar to Set-Cover.

\solution{}

1. Set-Cover is in NP.\\
Given a collection of subsets of $C$, and the integer $k$, we can visit each subset $C_i$, and mark the elements in $C_i$ as covered.\\ The visit would cost $O(k|C|)$ time, where $|C|$ is the number of elements in $|C|$. Then we check whether all elements in $C$ are covered.\\
So the total time complexity is $O((k+1)|C|)$, which is polynomial.\\
So Set-Cover $\in$ NP.\\

2. 3-SAT $\leq_p$ Set-Cover.\\
We can reduce 3-SAT to Set-Cover.\\
Given a 3-SAT problem, we can construct a Set-Cover problem.\\
Let the 3-SAT problem has $x_1,\cdots,x_n$ variables, $C_1,\cdots,C_m$ clauses, each clause has 3 literals.\\
We can construct the subsets:
Let $S_{x_i}$ to be clauses $C_j$ that $x_i$ appears in $C_j$.\\
Let $S_{\neg x_i}$ to be clauses $C_j$ that $\neg x_i$ appears in $C_j$.\\
And we can set $k$ to be the number of variables, if we can cover all the clauses.


<1> "$\Rightarrow$":\\
If 3-SAT has a yes instance, then each clause has at least one true literal. Choose the subsets corresponding to the literals that are true in the satisfying assignment. This selection covers all clauses, as each clause has at least one true literal by the definition of a satisfying assignment. So it is also a yes instance for the Set-Cover problem.

<2> "$\Leftarrow$":\\
If Set-Cover has a yes instance, which means that we can cover all clauses with at most n subsets. So there exists a selection of literals that covers every clause. Assign true to the literals selected in the solution and false to their complements. So it is also a yes instance for the 3-SAT problem.

<3> Polynomial Time:\\
The construction of the Set-Cover problem from the 3-SAT problem costs polynomial with $|V|$ and $|E|$ time.\\
Which is a polynomial time.\\

So we have proved that 3-SAT $\leq_p$ Set-Cover.\\

Since 3-SAT $\in$ NP-complete; Set-Cover $\in$ NP; 3-SAT $\leq_p$ Set-Cover.\\
Therefore, Set-Cover $\in$ NP-complete.\\

So above all, we have proved that Set-Cover is a NP-complete problem.

\newpage