\problem{}

Consider a list with $n$ unique positive integers, and suppose we iterate through the numbers one by one in a random order. As we do this, we maintain a variable $b$ equal to the largest number we have seen so far. Initially $b$ is set to 0 . Compute the expected number of times $b$ is updated.

For example, if the input list is $[4,7,5]$, and we iterate through the list in the order $3,1,2$, then $b$ is updated twice, when we see $5$ and $7$.
\solution{}
We firstly introduce a Lemma:
$$\sum\limits_{k=i}^n\binom{k-1}{i-1}=\binom{n}{i}$$
Proof of the Lemma:

1. When $n=i$, the left side of the equation is $\binom{i-1}{i-1}=1$, and the right side of the equation is $\binom{i}{i}=1$. The equation holds.

2. Suppose the equation holds when $n=m\geq i$, i.e.
$$\sum\limits_{k=i}^m\binom{k-1}{i-1}=\binom{m}{i}$$
then we need to prove the equation holds when $n=m+1$:
$$\sum\limits_{k=i}^{m+1}\binom{k-1}{i-1}=\sum\limits_{k=i}^{m}\binom{k-1}{i-1}+\binom{m}{i-1}=\binom{m}{i}+\binom{m}{i-1}=\binom{m+1}{i}$$
The equation holds when $n=m+1$.\\

So above all, we have proved the Lemma.\\

So for the list, since the numbers are unique, so W.L.O.G, we can assume the list is $[1,2,3,...,n]$.\\
Let the expected number of times $b$ is updated to be $E$.\\
So
\begin{align*}
    E &= \dfrac{1}{n!}\sum_{\text{$n!$ permutations}}\text{\# times $b$ is updated in this permutation} \\
    &= \dfrac{1}{n!}\sum_{\text{$n!$ permutations}}\sum_{i=1}^n\text{\# times $b$ is updated at the $i$-th number} \\
    &= \dfrac{1}{n!}\sum_{i=1}^n\sum_{\text{$n!$ permutations}}\text{\# times $b$ is updated at the $i$-th number} \\
    &= \dfrac{1}{n!}\sum_{i=1}^n\sum_{k=i}^n\binom{k-1}{i-1}(i-1)!(n-i)! \ \ \text{(let the $i$-th number is $k$, and it is the biggest among first $i$ numbers)} \\
    &= \dfrac{1}{n!}\sum_{i=1}^n(i-1)!(n-i)!\sum_{k=i}^n\binom{k-1}{i-1} \\
    &= \dfrac{1}{n!}\sum_{i=1}^n(i-1)!(n-i)!\binom{n}{i} \ \ \ \ \ \text{(Lemma)} \\
    &= \sum_{i=1}^n\dfrac{(i-1)!(n-i)!}{n!}\binom{n}{i} \\
    &= \sum_{i=1}^n\dfrac{i!(n-i)!}{n!}\binom{n}{i}\dfrac{1}{i} \\
    &= \sum_{i=1}^n\dfrac{1}{\binom{n}{i}}\binom{n}{i}\dfrac{1}{i} \\
    &= \sum_{i=1}^n\dfrac{1}{i} \\
    &= \log n + \gamma
\end{align*}

So above all, the expected number of times $b$ is updated is $\log n + \gamma$, where $\gamma$ is the Euler-Mascheroni constant.